
\fancyhead[R]{\slshape TÀI LIỆU THAM KHẢO}
\begin{thebibliography}{}

\bibitem{cfg-def}
Frances E. Allen. \emph{"Control flow analysis"}. SIGPLAN Notices 5 (7): 1–19. July 1970.

\bibitem{}
Nguyen Minh Hai, Mizuhito Ogawa and Quan Thanh Tho, \emph{"Obfuscation code localization based on CFG generation of malware"}.

\bibitem{}
Nguyen Minh Hai, Mizuhito Ogawa and Quan Thanh Tho, \emph{"Pushdown Model Generation of Malware"}, June 24th 2006.

\bibitem{}
Quan Thanh Tho, with Nguyen Minh Hai, in Collaboration with Mizuhito Ogawa, \emph{"BE – PUM: Binary Emulation for Pushdown Model Generation"}, a tool for under approximated model generation”, March 2015.	

\bibitem{}
Nguyen Minh Hai, with Quan Thanh Tho, in Collaboration with Mizuhito Ogawa, \emph{"Pushdown Model Generation for Malware Deobfuscation"}, March 2015.

\bibitem{}
Mizuhito Ogawa, with Nguyen Minh Hai, Quan Thanh Tho, \emph{"Pushdown model generation for binary code"}.

\bibitem{}
Nguyen Minh Hai, Nguyen Thien Binh, Quan Thanh Tho, and Mizuhito Ogawa, \emph{"A hybrid approach for control flow graph construction from binary code"}.

\bibitem{} 
Irvine, Kip R. \emph{"Assembly Language for x86 Processors"}, Prentice Hall, 2011. 

\bibitem{}
Hyde, Randall. \emph{"The art of assembly language"}, No Starch Press, 2010.

\bibitem{}
Corportation, Intel. \emph{"IA-32 Intel Architecture software developer’s manual"}, Intel Corportation (2001).

\bibitem{}
Tất cả thông tin về các câu lệnh x86, \emph{http://x86.renejeschke.de/html}.

\bibitem{}
Link tham khảo online: \emph{http://www.felixcloutier.com/x86/}.

\bibitem{}
Phép toán chuyển đổi \emph{http://www.exploringbinary.com/floating-point-converter/}.

\bibitem{}
Thông tin tổng quan về Windows API, \emph{http://en.wikipedia.org/wiki/Windows\_API}.

\bibitem{}
Thông tin chi tiết các Windows API, \emph{https://msdn.microsoft.com/en-us/library/cc433218(VS.85).aspx}.

\bibitem{}
Overview (JNA API), \emph{http://twall.github.io/jna/4.1.0/overview-summary.html}.

\bibitem{}
struct (C programming language), \emph{http://en.wikipedia.org/wiki/Struct\_\%28C\_programming\_language\%29}.

\end{thebibliography}